\section{Project Schedule and Milestones}

The schedule for this project is given in the
Tabel~\ref{table:timeline}.  We expect each topic to span
approximately 4 years of the project.  The total effort is evenly
distributed over the 5 year span of the project.

\begin{table}[h]
\begin{tabular}{||l|c|c|c|c|c|l||}
\hline\hline
{\bf Topic} & {\bf Y1} & {\bf Y2} & {\bf Y3} & {\bf Y4} & {\bf Y5} & {\bf PIs (lead in bold)}\\\hline\hline
Survivable network design & \multicolumn{4}{>{\columncolor[rgb]{0.650000,0.741000,0.858000}}r}{}  & &
%\multicolumn{1}{>{\columncolor[black]{0.8}}c}{} & 
%\multicolumn{1}{>{\columncolor[black]{0.8}}c}{} &
%\multicolumn{1}{>{\columncolor[black]{0.8}}c}{} &
%\multicolumn{1}{>{\columncolor[black]{0.8}}c}{} &
{\bf Ravi}, Rajaraman\\\hline
Stochastic aggregation tree problems & & \multicolumn{4}{>{\columncolor[rgb]{0.650000,0.741000,0.858000}}r}{} & {\bf Ravi}, Sundaram\\\hline
Universal aggregation trees  & \multicolumn{4}{>{\columncolor[rgb]{0.650000,0.741000,0.858000}}r}{}  & & {\bf Sundaram}, Rajaraman\\ \hline
Congestion-minimizing degree-bounded flows & & \multicolumn{4}{>{\columncolor[rgb]{0.650000,0.741000,0.858000}}r}{} & {\bf Sundaram}, Ravi\\ \hline
Information dissemination in adversarial networks & \multicolumn{4}{>{\columncolor[rgb]{0.650000,0.741000,0.858000}}r}{} &  & {\bf Rajaraman}, Ravi\\ \hline
\end{tabular}
\caption{Project timeline \label{table:timeline}}
\end{table}

\smallskip
\BfPara{Milestones} We will produce annual reports at the end of each
of the project years.  During the course of the project, we will
document all of the problem formulations and results in papers,
following ONR guidelines for publication.  At a high level, we will
have the following milestones for each of the topics.  For each
milestone, we include in parenthesis its deadline during the 4-year
period devoted to the topic:

\begin{itemize}
\item
{\sl Problem formulation:} Precise formulations for the core problem
and its variants.  (End of 1st year)
\item
{\sl Preliminary bounds:} Basic bounds on the competitive ratio. (End of 1st year) 
\item
{\sl Results for online models:} Results for suitable online stochastic and
online adversarial models. (End of 2nd and 3rd years)
\item
{\sl Decentralization:} Quantify the price of decentralization. (End of 4th year)
\end{itemize}

\section{Management Approach}

Management Approach: Bi-weekly coordination meetings, one face-to-face annual meeting, svn  repository for data, code and knowledge sharing, 


\section{Current and Pending Support}

Offerors are required to provide
information on all current and pending support for ongoing projects and proposals, including
subsequent funding in the case of continuing contracts, grants, and other assistance agreements.
Offerors shall provide the following information of any related or complementary proposal
submissions from whatever sources (e.g., ONR, Federal, State, local or foreign government
agencies, public or private foundations, industrial or other commercial organizations).

The information must be provided for all proposals already submitted or submitted concurrently
to other possible sponsors, including ONR. Concurrent submission of a proposal to other
organizations will not prejudice its review by ONR: 

1) Title of Proposal and Summary;\\
2) Source and amount of funding (annual direct costs; provide contract and/or
grant numbers for current contracts/grants);\\
3) Percentage effort devoted to each project;\\
4) Identity of prime Offeror and complete list of subcontractors/subreceipients, if
applicable;\\
5) Technical contact (name, address, phone/fax, electronic mail address)\\
6) Administrative/business contact (name, address, phone/fax, electronic mail
address);\\
7) Period of performance (differentiate basic effort);\\
8) The proposed project and all other projects or activities requiring a portion of
time of the Principal Investigator and other senior personnel must be included,
even if they receive no salary support from the project(s);\\


9) The total award amount for the entire award period covered (including indirect
costs) must be shown as well as the number of person-months or labor hours per
year to be devoted to the project, regardless of source of support; and\\

10) State how projects are related to the proposed effort and indicate degree of
overlap. 
