\subsection{Information Flow}
Our proposed work on decentralized network design will ensure that the
underlying communication network connecting the agent nodes satisfies
mission-critical connectivity properties.  The network structures thus
designed are very likely to change with time due to the mobility of
the nodes, failures in the communication links, as well as adversarial
attacks on the network.  The second major component of this proposal
to develop distributed algorithms for efficient and effective flow of
information over such dynamic networks.  Our proposed work on network
design allows us to make assumptions about minimal connectivity of the
underlying network; however, to guarantee high-throughput information
flow for a dynamic distributed environment, we need to control
congestion, and focus on local lightweight algorithms that maintain
limited state.  In this project, we will study two important
information flow problems: congestion-minimizing degree-bounded flows
(Section~\ref{sec:confluent}), and information spreading under
adversarial dynamics (Section~\ref{sec:spreading}).

\subsubsection{Congestion-minimizing degree-bounded flows in dynamic
  networks}
\label{sec:confluent}
A key requirement of scalable routing algorithms is to severely limit
the amount of information that each network node maintains; such
lightweight protocols are much more effective in a large-scale dynamic
setting.  Providing good guarantees on performance measures such as
congestion, however, then poses a major challenge.  In earlier work
\cite{awerbuch+l:flow}, distributed algorithms for finding congestion
minimizing flows in certain dynamic networks were presented.  However
the routes undertaken by these flows were unconstrained and expensive
to maintain.  We plan to build on our past work on efficient
algorithms for converting optimal flows into near-optimal {\em
  degree-bounded} flows~\cite{chen+klrsv:flow,chen+mrs:flow}; we call
a traffic flow $d$-bounded if all flow through a node $v$ destined for
a sink $t$ leaves $v$ through at most $d$ neighbors.  A small bound
for $d$ ensures that each node maintains very limited state per
destination.  Routing on the Internet is, in fact, $1$-bounded or
confluent~\cite{chen+mrs:flow}.  For reducing congestion in an ad-hoc
network environment, however, $d$-bounded flows for a small constant
$d$ will achieve significantly better performance.  Our current
algorithms for obtaining degree-bounded flows involve some refinement
techniques that require global knowledge.  We believe that the local
balancing approach of~\cite{awerbuch+l:flow}, in conjunction with our
flow refinement techniques, will enable us to maintain near-optimal
degree-bounded flows in dynamic networks.

\Research{
\label{prob:cmdf}
Design distributed algorithms for congestion-minimizing degree-bounded
multicommodity flows in dynamic networks.  }

We will begin with a stochastic model of traffic demand that assumes a
fixed rate of communication among the various source-destination
pairs, and a dynamic network model that bounds the rate of change of
the network.  We will then consider more adversarial models of
changing traffic demand and network dynamics assuming some minimum
network capacity, while ensuring that we maintain the degree-bound
constraint on the traffic flows.  We also plan to consider
generalizations of the problem incorporating link errors and coding
techniques.

\junk{
This problem can be generalized in a multiplicity of ways. Rather than
one commodity one can consider multiple commodities, each with their
own target or destination nodes. Second, one can consider the
availability of end-to-end capacities assuming duplex
connections.
 Third, one can assume different forms of error that
affect link capacities and the use of techniques such as network
coding. Finally, one can also consider integrating the route discovery
problem with the problem of optimizing the flows.
}


\subsubsection{Information spreading in adversarial networks}
\label{sec:spreading}
Problem~\ref{prob:cmdf} considers the task of routing point-to-point
multicommodity flows in networks with some restricted dynamics.  We
also plan to conduct a comprehensive study of fully distributed
algorithms for the more specialized task of information spreading in
highly dynamic networks controlled by adversaries.  In such scenarios,
the algorithms need to be lightweight, with each node continually
making decisions without any knowledge of the future, and possibly
even no information about the current network neighborhood.  Many
basic coordination tasks are very difficult or even impossible to
achieve in dynamic networks~\cite{fich+r:impossibility}.  We will
begin by studying the basic $k$-broadcast problem.  Recall that in the
$k$-broadcast problem, $k$ of the $n$ nodes each have a message that
need to be disseminated to every node in the network.  Suppose that
the nodes are synchronized and in each step, each node can broadcast
the equivalent of a bounded number of tokens to its
neighbors~\cite{kuhn+lo:dynamic}.  What is the minimum number of steps
needed to complete the dissemination?  If the network is completely
static and connected, then a local token-forwarding process on a
spanning tree of the network can accomplish the task in $O(n + k)$
steps, independent of the structure of the network.  In a dynamic
network as in the above model however, the problem is much more
challenging.

\Research{
\label{prob:broadcast}
Is there a distributed algorithm that completes any $k$-broadcast
instance in $O(n + k)$ steps on any adversarially dynamic $n$-node
network? }

In recent work~\cite{dutta+prs:dynamic}, we studied the class of {\em
  forwarding}\/ algorithms that do not manipulate tokens in any way
other than copying, storing, and forwarding them.  We show that {\em
  any}\/ forwarding algorithm will take $\Omega(nk/\log(n))$ steps to
complete $k$-broadcast, thus resolving an open problem
of~\cite{kuhn+lo:dynamic}.  Given that almost any local greedy
forwarding procedure completes $k$-broadcast in $O(nk)$ steps in any
dynamic network, our lower bound essentially captures the severe
limitations imposed by highly adversarial network dynamics.

A natural and attractive alternative to forwarding algorithms is to
use coding (either end-to-end~\cite{Byers02adigital,Shok06} or
network~\cite{ahlswede+cly:coding}).  Recent
work~\cite{haeupler:gossip,haeupler+k:dynamic} has shown that
information spreading based on network coding can solve $k$-broadcast
in $O(n+k)$ steps, assuming the sizes of the messages are $\Omega(n
\log n)$ bits.  While this message size lower bound is prohibitively
large and impractical (since it scales with the size of the network),
our lower bound~\cite{dutta+prs:dynamic} together with this upper
bound establish, in theory, a fundamental gap between flow-based and
coding-based dissemination procedures.

One approach we plan to pursue is to consider a hybrid
forwarding-coding algorithm in which nodes exchange information in the
symmetric difference of what they currently hold, which can be done in
$O(\log n)$ rounds of communication using
fingerprinting~\cite{mitzenmacher-2005-fastmixing}.  We have shown
that if the entropy of the initial distribution of information
is high, then convergence to full dissemination is rapid.  We will
also consider weaker notions of the adversary (e.g., offline or
oblivious), which model real-world settings where the adversary has
significant control but is not congnizant of all the network actions.
The offline dissemination problem can be reduced to the problem of
packing Steiner trees in directed
graphs~\cite{cheriyan+s:steiner,dutta+prs:dynamic}, and thus has deep
connections with the long-standing open problems of approximating
directed Steiner
trees~\cite{charikar+ccdgg:steiner,halperin+k:steiner,zosin+k:steiner}
and bounding the network coding advantage in multicast over directed
networks~\cite{agarwal+c:coding,sanders+et:flow}.

Following the $k$-broadcast problem, we will study more general
information spreading problems including consensus, computing
aggregates (that often arise in sensor network environments), and
larger classes of computations such as separable
functions~\cite{mosk-aoyama+s:separable}.

\Research{
\label{prob:dynamic_general}
Design and analyze fully distributed gossip-based algorithms for
consensus and aggregation, and computing separable functions. }

We expect to quantify all our results in terms of relevant parameters
including locality of the dynamics, conductance/expansion of the
evolving network, initial entropy of the information distribution, and
knowledge available to the dissemination algorithm.  

\iffalse*****
Repeats last para We have also shown that the dissemination problem
can be reduced to the problem of packing Steiner trees in directed
graphs, and thus has deep connections with the long-standing open
problems of approximating directed Steiner
trees~\cite{charikar+ccdgg:steiner} and bounding the network coding
advantage in multicast over directed networks.  \fi

