\section{Personnel Qualifications}

Prof. R. Ravi works in the intersection of Operations Research and
Computer Science and has pioneered work in various network
optimization problems such as the Buy-at-Bulk Network Design problem
with economies of scale, the Group Steiner Tree problem that combines
the Set Covering and Steiner Tree problems, and in designing provably
near-optimal approximation algorithms with performance guarantees for
problems in stochastic and robust combinatorial optimization. He has
also advanced the development of tools for the design of approximation
algorithms for network optimization such as the primal-dual method,
dependent randomized rounding, Lagrangean relaxations and iterative
methods.

Co-PI Rajaraman's research expertise covers distributed computing
theory, approximation algorithms, network optimization, and
algorithmic game theory.  His work on distributed hash tables is
widely-cited and has been implemented in several peer-to-peer network
systems.  Co-PI Sundaram's research expertise covers networks,
algorithms, complexity theory and combinatorics.  Before joining
academics, he was Director of Engineering at Akamai Technologies,
where he established the mapping group for the world's leading content
delivery network, which is responsible for directing browser requests
(over 10 billion a day) to the optimal Akamai server.

The PIs have a strong history of collaboration.  PI Ravi and co-PI
Sundaram were co-authors on a widely cited foundational paper on
bicriteria approximations in network design.  Co-PIs Rajaraman and
Sundaram were co-authors on a ICDCS 2006 paper on Internet capacity
that won the best paper award.  With deep synergistic expertise in
optimization theory, online and approximation algorithms, and
distributed computing, the team is uniquely positioned to address the
basic research challenges of this call.


